### 2018-12-04 tex/appendix.tex
Edited appendix - section on hierarchical Potts model.

\mysection{Proofs for Hierarchical Potts Model Extension} 
\myparagraph{Transformed Tightest LP Relaxation} We take (T-LP) and rewrite it using indicator variables for all labels and meta-labels. Let $\mathcal R$ denote the set of all labels and meta-labels, that is, all nodes in the tree apart from the root. Also, let $\mathcal L$ denote the set of labels, that is, the leaves of the tree. Let $T_i$ denote the subtree which is rooted at the $i$-th node. We introduce an indicator variable $z_{ai} \in \{0, 1\}$, where
\begin{align}
    \enskip  z_{ai} =  \begin{cases} 
        y_{ai} \quad &\text{if} \enskip i \in {\mathcal L} \\
        y_{a}(T_i) \quad &\text{if} \enskip i \in {\mathcal R - \mathcal L} \\
    \end{cases}
\end{align}

We need to extend the definition of unary potentials to the expanded label space as follows:
\begin{align}
    \text{where} \enskip    \phi'_{a}(i) =  \begin{cases} 
        \phi_{a}(i) \quad &\text{if} \enskip i \in {\mathcal L} \\
        0  \quad &\text{if} \enskip i \in {\mathcal R - L} \\
    \end{cases}
\end{align}
%
We can now rewrite problem \eqref{eq:t-lp} in terms of new indicator variables $z_{ai}$:
%
\begin{align}
    \text{(T-LP-FULL)} \quad &\min \widetilde{E}({\bf z}) = \sum_{i \in \mathcal{R}} \sum_{a \in {\mathcal X}} \phi_a'(i) \cdot z_{ai} + \nonumber \\
            &\sum_{i \in \mathcal{R}} \sum_{(a, b) \in {\mathcal N}} w_{ab} \cdot l_{T_i} \cdot |z_{ai} - z_{bi}| \nonumber \\
    \text{such that} \quad {\bf z} \in \Delta'
%\label{eq:t-lp-full}
\end{align}
   where $\Delta'$ is the convex hull of the vectors satisfying
\begin{align}
    \enskip &\sum_{i \in \mathcal{L}} z_{ai} = 1, \enskip z_{ai} \in \{0, 1\} \enskip \forall a \in {\mathcal X}, i \in \mathcal{L} \\
    \text{and} \enskip &z_{ai} = \sum_{j \in L(T_i) } z_{aj}.\enskip \forall a \in {\mathcal X}, i \in \mathcal{R - L} %\label{eq:consistency_constraint} 
\end{align}
%
Constraint (\ref{eq:consistency_constraint}) ensures consistency among labels and meta-labels, that is, if a label is assigned then all the meta-labels which lie on the path from the root to the label should be assigned as well. We are now going to identify a suitable set encoding and the worst-case optimal submodular extension using (T-LP-FULL).

@@

\begin{proof}
In the limit of $T \to 0$, we can rewrite the above problem as
\begin{equation}
    \min_{{\bf s} \in EP(F)} \quad \sum_{a = 1}^{N} \max_{i} (-s'_{ai}).
\end{equation}
In vector form, the problem becomes
\begin{align}
    &\min_{{\bf s} \in EP(F)} \max_{{\bf z} \in \Delta} - \langle {\bf z}, {\bf s'} \rangle \\
    & = - \max_{{\bf s} \in EP(F)} \min_{{\bf z} \in \Delta} \langle {\bf z}, {\bf s'} \rangle
    %\label{eq:metric_maxmin}
\end{align}
\begin{equation}
    \text{where } \Delta = \{{\bf z}_a \in \mathbb{R}^L | {\bf z}_a \succeq 0  \textrm{ and } \langle {\bf 1}, {\bf z}_a \rangle = 1\}
\end{equation}
where ${\bf z}_a$ is the component of $\bf z$ corresponding to the $a$-th variable. We can unpack $\bf s'$ using 
\begin{equation}
s'_{ai} = \sum_{t \in p_{ai}} s_t.
%\label{eq:tree_s}
\end{equation}
and rewrite problem \eqref{eq:metric_maxmin} as
\begin{align}
    - \max_{{\bf s} \in EP(F)} \min_{{\bf y} \in \Delta'} \langle {\bf y}, {\bf s} \rangle
    %\label{eq:metric_maxmin_unpack}
\end{align}
The new constraint set $\Delta'$ ensures that the binary entries of labels and meta-labels is consistent:
\begin{align}
    \textrm{where } \Delta' &= \{ {\bf y}_a \in \mathbb{R}^M | {\bf y}_a \succeq 0, \enskip \langle {\bf 1}, {\bf y}_a^{label} \rangle = 1, \nonumber \\
    &\enskip {\bf y}_a(p_{ai}) = {\bf 1} \textrm{ or } {\bf y}_a(p_{ai}) = {\bf 0} \forall i \in [1, L]\}
\end{align} 
where ${\bf y}_a$ is the component of $\bf y$ corresponding to the $a$-th variable, ${\bf y}_a^{label}$  is the component of ${\bf y}_a$ corresponding to the $L$ labels, and ${\bf y}_a(p_{ai})$ is the component of ${\bf y}_a$ corresponding to the elements of $p_{ai}$.

@@

{\proposition The objective function $\widetilde{E}({\bf z})$ of (T-LP-FULL) is the Lovasz extension of $F_{r-\textrm{HST}}(A) = \sum_{i = 1}^M F_i(A)$, where
\begin{align}
    F_i(A) &= \sum_a \phi'_{a}(i) [|A \cap \{v_{ai}\}| = 1] + \nonumber \\
           &\sum_{(a, b) \in {\mathcal N}} {w_{ab}} \cdot l_{T_i} \cdot [|A \cap \{v_{ai}, v_{bi}\}| = 1]
\end{align}
%\label{proposition:rhst_optimal}}
\begin{proof}
    We observe that $F_{r-\textrm{HST}}$ is of exactly the same form as $F_{Potts}$, except that the Ising models $F_i$ are defined over not just labels, but meta-labels as well. Using the same logic as in the proof of proposition \ref{proposition:a-potts_optimal}, each $F_i$ is the Lovasz extension of 
        \begin{equation}
            \widetilde{E}_i({\bf z}) = \left( \sum_{a \in {\mathcal X}} \phi_a'(i) \cdot z_{ai} + \sum_{(a, b) \in {\mathcal N}} w_{ab} \cdot l_{T_i} \cdot |z_{ai} - z_{bi}| \right)
        \end{equation}
    and the results follows. 
\end{proof}
\iffalse
\section{Additional Experiment Results}

>>>>

\mysection{Proofs for Hierarchical Potts Model Extension}

@@

\begin{proof}
In the limit of $T \to 0$, we can rewrite the above problem as
\begin{equation}
    \min_{{\bf s} \in EP(F)} \quad \sum_{a = 1}^{N} \max_{i} (-s'_{ai}).
\end{equation}
In vector form, the problem becomes
\begin{align}
    &\min_{{\bf s} \in EP(F)} \max_{{\bf z} \in \Delta} - \langle {\bf z}, {\bf s'} \rangle \\
    & = - \max_{{\bf s} \in EP(F)} \min_{{\bf z} \in \Delta} \langle {\bf z}, {\bf s'} \rangle
    \label{eq:metric_maxmin}
\end{align}
\begin{equation}
    \text{where } \Delta = \{{\bf z}_a \in \mathbb{R}^L | {\bf z}_a \succeq 0  \textrm{ and } \langle {\bf 1}, {\bf z}_a \rangle = 1\}
\end{equation}
where ${\bf z}_a$ is the component of $\bf z$ corresponding to the $a$-th variable. We can unpack $\bf s'$ using 
\begin{equation}
s'_{ai} = \sum_{t \in p_{ai}} s_t.
%\label{eq:tree_s}
\end{equation}
and rewrite problem \eqref{eq:metric_maxmin} as
\begin{align}
    - \max_{{\bf s} \in EP(F)} \min_{{\bf y} \in \Delta'} \langle {\bf y}, {\bf s} \rangle
    %\label{eq:metric_maxmin_unpack}
\end{align}
The new constraint set $\Delta'$ ensures that the binary entries of labels and meta-labels is consistent:
\begin{align}
    \textrm{where } \Delta' &= \{ {\bf y}_a \in \mathbb{R}^M | {\bf y}_a \succeq 0, \enskip \langle {\bf 1}, {\bf y}_a^{label} \rangle = 1, \nonumber \\
    &\enskip {\bf y}_a(p_{ai}) = {\bf 1} \textrm{ or } {\bf y}_a(p_{ai}) = {\bf 0} \forall i \in [1, L]\}
\end{align} 
where ${\bf y}_a$ is the component of $\bf y$ corresponding to the $a$-th variable, ${\bf y}_a^{label}$  is the component of ${\bf y}_a$ corresponding to the $L$ labels, and ${\bf y}_a(p_{ai})$ is the component of ${\bf y}_a$ corresponding to the elements of $p_{ai}$.

@@

{\proposition The objective function $\widetilde{E}({\bf z})$ of (T-LP-FULL) is the Lovasz extension of $F_{r-\textrm{HST}}(A) = \sum_{i = 1}^M F_i(A)$, where
\begin{align}
    F_i(A) &= \sum_a \phi'_{a}(i) [|A \cap \{v_{ai}\}| = 1] + \nonumber \\
           &\sum_{(a, b) \in {\mathcal N}} {w_{ab}} \cdot l_{T_i} \cdot [|A \cap \{v_{ai}, v_{bi}\}| = 1]
\end{align}
%\label{proposition:rhst_optimal}}
\begin{proof}
    We observe that $F_{r-\textrm{HST}}$ is of exactly the same form as
    $F_{Potts}$, except that the Ising models $F_i$ are defined over not just labels, but meta-labels as well. Using the same logic as in the proof of Potts extension, each $F_i$ is the Lovasz extension of 
        \begin{equation}
            \widetilde{E}_i({\bf z}) = \left( \sum_{a \in {\mathcal X}} \phi_a'(i) \cdot z_{ai} + \sum_{(a, b) \in {\mathcal N}} w_{ab} \cdot l_{T_i} \cdot |z_{ai} - z_{bi}| \right)
        \end{equation}
    and the results follows. 
\end{proof}
\iffalse
\section{Additional Experiment Results}
